% run as XeLaTeX
%!TEX TS-program = xelatex
\documentclass[44pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper, margin=0.8in}                   		% ... or a4paper or a5paper or letterpaper or... 
%\geometry{landscape}                		% Activate for rotated page geometry
\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex	

\usepackage{hyperref}				% enabled hyperlink support	
%\usepackage{amssymb}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
    
\input{../commands/kanjicommands}

\title{\vspace{-2.0cm}Japanese Intermediate 1}
\date{\vspace{-1.0cm}\fgdate{2022}{10}{4}{よっか} }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\maketitle{}

\href{https://padlet.com/coachingteam/2806zrpg7nt2okgi}{PADLETのハイパーリンク}

% we use \protect for fragile (parameterised) commands that may get moved to other places in the document (e.g. section -> table of contents)
\section*{\protect \fg{漢字}{かんじ}や\fg{単語}{たんご}。(kanji and vocab)}

\begin{tabular}{l l l }

\fg{動物}{どうぶつ}（animal） &  \fg{会話}{かわい}（conversation）& \fg{練習}{れんしゅう}（practise/training）\\

\end{tabular}

\section*{\protect \fg{文法}{ぶんぽう}。(grammar)}

\subsection*{\protect Continuing action in the past (again)}

V-ていました。/ V-ていましたか。

\fg{昨日}{きのう}、\fg{公園}{こうえん}でどうしていましたか。（What were you doing in the park yesterday?）

\subsection*{\protect V-\fg{可能系}{かのうけい}とて (potential form + てform)}

V-（られ）て、＿＿＿＿ 。/ V-（られ）なくて、＿＿＿＿ 。(giving a reason for/cause of one's feelings)

\fg{親}{おや}に\fg{会}{あ}えて、よかったです。（It was good, that I was able to meet my family.）

\fg{友達}{ともだち}に、\fg{会}{あ}えなくて、\fg{残念}{ざんねん}でした。（It was disappointing that I wasn't able to meet my friends.）

\section*{\protect \fg{質問}{しつもん}で\fg{会話}{かいわ}の\fg{燃焼}{れんしゅう}することについては。(conversation question practise)}

Example questions (\textit{with no particular theme}):

\fg{暗殺者}{あんさつしゃ}になることは\fg{如何}{どう}でしたか。（How did you become an assassin?）

これは\fg{誰}{だれ}のナイフですか。（Whose knife is this?）

だれと\fg{刑務所}{けいむしょ}に\fg{行}{い}きますか。（Who are you going to prison with?）

どんなナイフが\fg{一番}{いちばん}\fg{好}{す}きですか。（what is your favourite type of knife?）

どうしてリトアニアに\fg{行}{い}きましたか。（Why did you go to Lithuania?）

\fg{昨日}{きのう}、\fg{実験所}{じっけんしょ}でどうしていましたか。（What were you doing in the research facility yesterday?）

\fg{警官}{けいかん}はどこにいりますか。（Where are the police officers?）

オリエント\fg{急行}{きゅうこう}は\fg{何時}{なんじ}にイスタンブールに\fg{着}{つ}きますか。（What time does the Orient Express reach Istanbul?）

\fg{李}{すもも}\fg{先生}{せんせい}はいつ\fg{死}{し}にましたか。（When did Professor Plum die?）







\end{document}  